\chapter{APPENDIX}

\section{Key Dependencies}
\renewcommand{\arraystretch}{1.3}
\begin{longtable}{|p{5cm}|p{3cm}|p{5cm}|}
    \hline
    \textbf{Package} & \textbf{Version} & \textbf{Purpose} \\
    \hline
    \endfirsthead
    \hline
    \textbf{Package} & \textbf{Version} & \textbf{Purpose} \\
    \hline
    \endhead
    \hline
    \endfoot
    \hline
    \caption{PHP (Composer) Dependencies} \label{tab:php_deps} \\
    \endlastfoot
    laravel/framework & \^{}11.0 & Core web framework \\
    \hline
    laravel/breeze & \^{}2.0 & Auth scaffolding \\
    \hline
    laravel-socialite & \^{}5.0 & Google OAuth \\
    \hline
    inertiajs/inertia-laravel & \^{}2.0 & Inertia.js server adapter \\
    \hline
    tightenco/ziggy & \^{}2.0 & Laravel routes in JS \\
    \hline
\end{longtable}

\renewcommand{\arraystretch}{1.3}
\begin{longtable}{|p{5cm}|p{3cm}|p{5cm}|}
    \hline
    \textbf{Package} & \textbf{Version} & \textbf{Purpose} \\
    \hline
    \endfirsthead
    \hline
    \textbf{Package} & \textbf{Version} & \textbf{Purpose} \\
    \hline
    \endhead
    \hline
    \endfoot
    \hline
    \caption{JavaScript (NPM) Dependencies} \label{tab:js_deps} \\
    \endlastfoot
    react & \^{}18.2.0 & UI component library \\
    \hline
    @inertiajs/react & \^{}2.0.0 & Inertia React adapter \\
    \hline
    tailwindcss & \^{}3.2.1 & Utility-first CSS framework \\
    \hline
    vite & \^{}7.0.0 & Build tool and dev server \\
    \hline
    gsap & \^{}3.14.2 & Animation library \\
    \hline
    react-hot-toast & \^{}2.6.0 & Toast notifications \\
    \hline
    axios & \^{}1.11.0 & HTTP client \\
    \hline
\end{longtable}

\section{Glossary}
\begin{itemize}
    \item \textbf{MVC} -- Model-View-Controller: a software architectural pattern.
    \item \textbf{ORM} -- Object-Relational Mapper: a technique for mapping database rows to objects.
    \item \textbf{SPA} -- Single-Page Application: a web app that dynamically rewrites the current page rather than loading entire new pages from the server.
    \item \textbf{Inertia.js} -- A library that allows building monolithic SPA-like applications using server-side routing and controllers.
    \item \textbf{SMTP} -- Simple Mail Transfer Protocol: the email transmission protocol.
    \item \textbf{OAuth} -- Open Authorization: an open standard for access delegation.
    \item \textbf{GSAP} -- GreenSock Animation Platform: a robust JavaScript animation library.
    \item \textbf{CRUD} -- Create, Read, Update, Delete: the four basic database operations.
    \item \textbf{HMR} -- Hot Module Replacement: a Vite feature for instant module reloading during development.
    \item \textbf{COD} -- Cash on Delivery: a payment method where payment is made at the time of delivery.
\end{itemize}
