\chapter{INTRODUCTION}

\section{Overview}
Francs is a full-stack e-commerce web application developed to offer a user-friendly online shopping experience for fashion and lifestyle products. The platform caters to two primary user groups: customers who browse and purchase products, and administrators who manage the store's inventory, orders, and users. Built on modern web technologies, Francs brings together a polished frontend experience with a robust backend business logic layer.

\section{Purpose of the Project}
The primary purpose of Francs is to create a scalable, maintainable, and feature-rich e-commerce platform from scratch. Existing platforms often have high licensing costs or limited customization. Francs addresses this by providing a custom-built solution leveraging open-source technologies, allowing full control over every aspect of the business workflow --- from product listing to order fulfillment and customer communication.

\section{Scope}
The scope of the Francs project includes:
\begin{itemize}
    \item A public-facing storefront with product browsing, filtering, searching, and sorting features.
    \item A customer account system with Google OAuth and email/password authentication.
    \item A session-based shopping cart and multi-step checkout flow.
    \item Automatic order confirmation emails sent on successful checkout.
    \item A product review and rating system.
    \item An admin dashboard for managing products, categories, orders, customers, and vendors.
    \item Activity logging to track admin actions.
    \item A community page for brand engagement.
\end{itemize}

\section{Technology Stack}
The Francs platform uses the following technologies:
\begin{itemize}
    \item \textbf{Backend Framework:} Laravel 11 (PHP)
    \item \textbf{Frontend Layer:} React 18 with Inertia.js (SPA-style navigation)
    \item \textbf{Styling:} Tailwind CSS v3
    \item \textbf{Build Tool:} Vite
    \item \textbf{Database:} SQLite (development) / MySQL (production)
    \item \textbf{Email:} Laravel Mail (SMTP via Mailtrap / production SMTP)
    \item \textbf{Authentication:} Laravel Breeze + Google OAuth
    \item \textbf{Animation Library:} GSAP v3
\end{itemize}
