\chapter{DEPLOYMENT}

\section{Project Folder Structure}
The Francs project follows the standard Laravel application directory structure with React components organised under \texttt{resources/js}:

\begin{itemize}
    \item \textbf{app/} -- PHP application logic:
        \begin{itemize}
            \item \texttt{Http/Controllers/} -- Application request handlers.
            \item \texttt{Models/} -- Eloquent ORM database entities.
            \item \texttt{Mail/} -- Email notification classes (e.g., \texttt{OrderPlaced}).
            \item \texttt{Providers/} -- Service registration logic.
        \end{itemize}
    \item \textbf{resources/js/} -- React frontend:
        \begin{itemize}
            \item \texttt{Pages/} -- Full-page React components (Home, Shop, Admin).
            \item \texttt{Components/} -- Shared UI elements (CustomDropdown, CartItem).
            \item \texttt{Layouts/} -- Shared page templates (Authenticated, Guest).
        \end{itemize}
    \item \textbf{resources/views/} -- Static Blade root (\texttt{app.blade.php}) and Email templates.
    \item \textbf{routes/} -- Endpoint definitions (\texttt{web.php}, \texttt{auth.php}, \texttt{console.php}).
    \item \textbf{database/} -- Migrations, Seeders, and factory definitions.
    \item \textbf{public/} -- Storage symlinks, entry point (\texttt{index.php}), and compiled assets.
    \item \textbf{config/} -- Global configuration files (app, database, mail, inertia).
    \item \textbf{storage/} -- Private log files, session files, and uploaded product images.
    \item \textbf{vite.config.js} -- Build pipeline configuration for Laravel and React.
    \item \textbf{package.json} -- Frontend dependencies (React, GSAP, Tailwind, Inertia).
    \item \textbf{composer.json} -- Backend dependencies (Laravel, Socialite, Breeze).
\end{itemize}

\section{Local Development Setup}
To run the Francs application locally, the following commands are executed:

\begin{lstlisting}[style=phpstyle]
# Install PHP dependencies
composer install

# Install Node.js dependencies
npm install

# Set up environment
cp .env.example .env
php artisan key:generate

# Run database migrations
php artisan migrate

# Start the Laravel development server
php artisan serve

# Start the Vite dev server (in a separate terminal)
npm run dev
\end{lstlisting}

\section{Environment Configuration}
Key \texttt{.env} variables required for the Francs application:

\begin{lstlisting}[style=phpstyle]
APP_NAME=FRANCS
APP_URL=http://localhost

DB_CONNECTION=pgsql
DB_HOST=127.0.0.1
DB_PORT=5432
DB_DATABASE=your_database_name
DB_USERNAME=postgres
DB_PASSWORD=your_db_password

MAIL_MAILER=smtp
MAIL_HOST=smtp.gmail.com
MAIL_PORT=587
MAIL_USERNAME=your_gmail_address
MAIL_PASSWORD=your_gmail_app_password
MAIL_ENCRYPTION=tls
MAIL_FROM_ADDRESS="your_gmail_address"
MAIL_FROM_NAME="${APP_NAME}"

GOOGLE_CLIENT_ID=your_google_client_id
GOOGLE_CLIENT_SECRET=your_google_client_secret
GOOGLE_REDIRECT_URI=http://localhost:8000/auth/google/callback

CLOUDINARY_API_KEY=your_cloudinary_api_key
CLOUDINARY_API_SECRET=your_cloudinary_api_secret
CLOUDINARY_CLOUD_NAME=your_cloudinary_cloud_name
CLOUDINARY_URL=cloudinary://api_key:api_secret@cloud_name
\end{lstlisting}

\section{Production Build}
To generate optimized production assets:

\begin{lstlisting}[style=phpstyle]
npm run build
php artisan config:cache
php artisan route:cache
php artisan view:cache
\end{lstlisting}

The compiled assets are written to \texttt{public/build/} and referenced by the Blade root template. The application can be deployed to any standard PHP 8.2+ hosting environment (Apache/Nginx with PHP-FPM).
