\chapter{CONCLUSIONS}

The Francs e-commerce platform has been successfully developed as a full-stack web application that demonstrates a complete online retail workflow, from product browsing and cart management to secure checkout, automated email notifications, and admin management.
\\\\
The project leverages a modern and highly productive technology stack: \textbf{Laravel 11} provides a robust backend with Eloquent ORM, authentication (email + Google OAuth), and mail delivery; \textbf{React 18 with Inertia.js} delivers a fluid, SPA-like frontend experience without the complexity of a separate API; and \textbf{Tailwind CSS} with \textbf{GSAP} provides a polished, responsive, and animated user interface.
\\\\
Key achievements of the project include:
\begin{itemize}
    \item A complete product catalogue with search, filter, and sort functionality.
    \item A session-based cart system requiring no dedicated database table.
    \item A transactional checkout flow with COD and card payment method support.
    \item Automatic order confirmation emails sent via Laravel Mail.
    \item A comprehensive admin dashboard with activity logging.
    \item Product reviews and star ratings submitted by verified users.
    \item Dual authentication (email/password and Google OAuth).
\end{itemize}
The Francs platform demonstrates that a scalable, professional-grade e-commerce application can be built entirely with open-source technologies at minimal cost, making it suitable for real-world deployment and further commercial development.
