\chapter{FUTURE WORKS}

While the Francs e-commerce platform provides a comprehensive foundation for online retail, several enhancements are planned for future development:

\begin{itemize}
    \item \textbf{Payment Gateway Integration:} Integrate a production-ready payment gateway such as Stripe or Razorpay to replace the current placeholder payment method simulation, enabling real credit card and digital wallet transactions.

    \item \textbf{Wishlist Feature:} Allow users to save products to a persistent wishlist stored in the database, enabling cross-device access to saved items.

    \item \textbf{Product Variants:} Support for product variations (e.g., size, color) with separate stock tracking per variant, essential for a fashion e-commerce platform.

    \item \textbf{Real-Time Order Tracking:} Implement a live order tracking page where customers can follow the status of their order from placement through shipping to delivery.

    \item \textbf{Push Notifications:} Add browser push notifications for order status updates, restocking alerts, and promotional announcements.

    \item \textbf{Multi-Vendor Support:} Expand the platform to support multiple independent vendors, each managing their own product listings, orders, and payouts, transforming Francs into a marketplace.

    \item \textbf{Search Engine Optimization:} Implement server-side rendering for public product pages to improve SEO indexing and improve organic discovery.

    \item \textbf{Customer Loyalty Program:} Introduce a points-based reward system where customers earn points on purchases and redeem them for discounts.

    \item \textbf{Analytics Dashboard:} Provide the admin with a visual analytics dashboard displaying revenue trends, top-selling products, customer demographics, and conversion rates.

    \item \textbf{Mobile Application:} Develop a companion mobile application (iOS/Android) using React Native that connects to a dedicated Laravel REST API.
\end{itemize}
